---
title: "Practical Machine Learning Project"
output:
  html_document:
    df_print: paged
---

Load Data. Remove empty rows. Describe Data.
```{r}

training_dat = read.csv("C:/Users/Pulin CTR Jhaveri/Downloads/pml-training.csv", na.strings=c("NA","","#DIV/0!"))
training_dat = training_dat[,colSums(is.na(training_dat))==0]  

testing_dat = read.csv("C:/Users/Pulin CTR Jhaveri/Downloads/pml-testing.csv", na.strings=c("NA","","#DIV/0!"))
testing_dat = testing_dat[,colSums(is.na(testing_dat))==0]  

head(training_dat)
str(training_dat)
dim(training_dat)


```


For Cross Validation: We will sub-divide training into 2 subsets. subtrain and validation
```{r}

library(caret)

subtrainList<-createDataPartition(training_dat$classe, p = 0.6, list = FALSE)
subtrain<-training_dat[subtrainList,]
validation<-training_dat[-subtrainList,]
head(subtrain)
preObj <- preProcess(subtrain, method=c("center","scale"))

```

preprocessing and train the model
```{r}
colnames(subtrain)
modFit <- train(classe ~ ., data = subtrain, method = "rf",preProcess=c("center","scale"))
print(modFit)


```

Predict on the validation Set
```{r}
validation_predict<-predict(modFit,validation)

validation$classe = factor(validation$classe)
confusionMatrix(validation_predict,validation$classe)

```

As we can see the Accuracy is 0.9999 and Out-of-Sample error rate is 1-0.9999=0.0001
With this level of accuracy, we can say that our model is modest.

Important Variables:
```{r}
varImp(modFit)

```

Use this model to fit the testing cases:
```{r}
predict_test_final<-predict(modFit,testing_dat)
print(predict_test_final)
```